\documentclass[11pt]{amsart}
\usepackage[margin=.5in]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{paralist}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Duncan College Article: Room Jack}
\author{Duncan College}
%\date{}                                           % Activate to display a given date or no date

\begin{document}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Bed Allocation Procedure}
\begin{enumerate}
	\item Student Classification
		\begin{enumerate}
		\item Students shall be eligible to be kicked off campus if they are not bump-exempt.
		\item The class of a student shall be the graduation year of their matriculating class, withexception for students who transferred into Rice University from another University. Theclass of a transfer student shall be their projected graduation year.
		\item Bump-exempt students shall be Seniors who have declared their Senior Status withthe College, incoming Freshmen, individuals who has lived off campus for at least onesemester in the previous academic year, and varsity scholarship athletes.
		\item The Senior Status is automatically declared for a student's fourth year at Rice. A studentmay, with permission of the Masters, defer their senior status by up to one year if andonly if they enter the bed allocation draw for that year.
		\item Students who remain Rice Students after declaring their Senior Status shall be classifiedas post-Senior students and shall not be eligible to enter the Bed Allocation process.
		\item A student may be classified as bump- exempt under special allowance if they satisfy oneof the following:
			%%%%%%%%%%%%%%%%%%%%
			\begin{enumerate}
				\item Documented medical consideration that requires that a student live on campus				\item Documented medical consideration in which a student’s quality of life would be significantly lower living off-campus solely due to the medical consideration				\item Extenuating circumstances that compromise a student’s safety outside of thenormal risks associated with living and being a Rice Student
			\end{enumerate}
		\item All conditions for a student to be classified as bump-exempt under special allowancemust be thoroughly substantiated to the Masters, communicating the condition satisfiedto the Legislative Vice President.		\item Any student who receives a room from the draw but decides to relinquish the room shallbe classified as bump-exempt in the subsequent year if and only if another student takes their place; for the student to receive a bump-exempt status in the subsequent year, the room may not be left vacant.
		\end{enumerate}
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Procedure}
\begin{enumerate}
	\item The procedure for bed allocation shall be determined by the Legislative Vice President. It must satisfy the following conditions. The procedure must be:
		\begin{enumerate}
		\item Accessible to all current students		\item Demonstrably fair and unbiased
		\end{enumerate}
	\item The Legislative Vice President will post two weeks in advance the procedure to be usedfor the Bed Allocation Process if any changes from the previous year occur.
	\item The Bed Allocation Procedure must include the following:
		\begin{enumerate}
			\item A waiting list containing the following properties:
				\begin{enumerate}
					\item Students kicked off in the Bed Allocation Draw (randomly ordered)?					\item Students who elected to move off-campus and wish to instead live on campus for the following year (ordered by time-stamp of official communication)
				\end{enumerate}
			\item Accessible and available to all Duncan Students
		\end{enumerate}
	\item The draw shall be conducted publicly at a time most students can attend	\item Any student failing to submit all required forms for the draw shall not be allowedto enter the draw	\item Students shall be kicked off from the rising-sophomore class and rising-juniorclass	\item The number of students kicked from each class shall be equal in proportion tothe proportional size of each of the classes from which students may be kicked


\end{enumerate}


\end{document}  